COG-ED Manuscript

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
excluded post-error trials and reaction times below 200 ms

```{r setup, include=FALSE}

@@

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}

  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
# we could add the package versions here additionally

@@

>>>>

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

@@

@@

  # exclude trials after incorrect responses

  data_nback <- data_nback[-c(which(data_nback$correct == 1) + 1), ]

  # exclude trials with reaction times below 200 ms

  data_nback <- data_nback[-c(which(data_nback$rt < 0.2)), ]
